---
title: "Proposal"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

### Group member
* Binyue Hu bh2849
* Hengxuan Ma hm2900
* Xin Ren xr2160
* Sophie Chen jc5924

### Tentative project title
* NYC leading causes of death 

### The motivation for the project
* Recently one of our team members has heard that COVID-19 become the second leading cause of death for New York state.
https://www.cdc.gov/nchs/pressroom/states/newyork/ny.htm#lcod
* We are interested in what the other leading causes of death are, especially in the city of New York where we are currently living. In this project, we intended to explore NYC's leading causes of death dataset and NCHS leading causes of death United States dataset.

### The intended final products 
* A report summarizing exploratory analysis results, recommendation algorithms used, and predicted leading causes related deaths in NYC	
* A wonderful dashboard giving movie details about the relationship between leading causes and deaths.

### The anticipated data sources
* New York City Leading Causes of Death https://data.cityofnewyork.us/Health/New-York-City-Leading-Causes-of-Death/jb7j-dtam
* NCHS - Leading Causes of Death: United States https://catalog.data.gov/dataset/nchs-leading-causes-of-death-united-states

### The planned analyses/visualizations/coding challenges
- The biggest challenge is that there is too little reference data
- Comparisons between causes of death in different places are difficult
- Difficulties in merging different data tables and clear the data
- The causes of death are too widely distribution

### The planned timeline
```{r}
data.frame(Date=c("Nov 8","Nov 8-10","Nov 12","Nov 13-14","Nov 15-18","Nov 30","Dec 4","Dec 10","Dec 10","Dec 12-14","Dec 15"),
           Description=c("Brainstorm","Together work on proposal","Submit the proposal","Distribute tasks","Project reviewing meeting","Finish the coding part","Start to construct a webpage","Report&webpage and screencast","Peer assessment","Practice for presentation","In class discussion of project"),
           Due=c("NA","NA","Nov 12 1:00 pm","NA","Nov 15-18","NA","NA","Dec 10 11:59 pm","Dec 10 11:59 pm","NA","Dec 15"))
```








