---
title: "Proposal"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

### Group member
* Binyue Hu bh2849
* Hengxuan Ma hm2900
* Xin Ren xr2160
* Sophie Chen jc5924

### Tentative project title
* NYCPD Complaint Data Historic  

### The motivation for the project
* It is the fact that all of our team members have heard crime alerts from NYPD frequently. We have been so curious about the detailed information of historical crimes happened in the New York City, especially in the pattern where we are currently living. 

* Since in recent years COVID-19 brought huge effects to people's life, We are interested in the changes of complaint numbers each year from 2020 to 2021, especially in the Manhattan borough. In this project, we intended to explore the general information about complaint data in the past two years, and to figure out if COVID-19 influenced the rate or other attributes of crimes.

### The intended final products 
* A report summarizing analysis results on the comparisons of NYPD compliant data between 2020 and 2021.
* A dashboard providing tips and recommendations for physical and mental health, and some details about the relationship between leading causes and deaths will be given.
* An "instagram filter" has random death causes popping up with recommended algorithms used.

### The anticipated data sources
* NYCPD Complaint Data Historic
https://data.cityofnewyork.us/Public-Safety/NYPD-Complaint-Data-Historic/qgea-i56i

### The planned analyses/visualizations/coding challenges
- The biggest challenge is that the raw data is too large to be analyzed and uploaded
- Comparisons between NYPD complaint data in different years based on plenty of variables are difficult
- Difficulties in clearing the data and selecting meaningful information

### The planned timeline
```{r}
data.frame(Date=c("Nov 8","Nov 8-10","Nov 12","Nov 13-14","Nov 15-18","Nov 30","Dec 4","Dec 10","Dec 10","Dec 12-14","Dec 15"),
           Description=c("Brainstorm","Together work on proposal","Submit the proposal","Distribute tasks","Project reviewing meeting","Finish the coding part","Start to construct a webpage","Report&webpage and screencast","Peer assessment","Practice for presentation","In class discussion of project"),
           Due=c("NA","NA","Nov 12 1:00 pm","NA","Nov 15-18","NA","NA","Dec 10 11:59 pm","Dec 10 11:59 pm","NA","Dec 15")) %>% 
  knitr::kable()
```








